---
title: "TA_WilsonFlies"
author: "Tyler Audet"
date: "19/09/2022"
output: 
  html_document: 
    toc: yes
    number_sections: yes
    keep_md: yes
editor_options: 
  chunk_output_type: console
---

# Data clean up and Analysis for morphological measurements Gen75

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyr)
library(skimr)
library(ggplot2)
library(ggbeeswarm)
library(ggridges)
library(glmmTMB)
library(emmeans)
library(effects)
library(dotwhisker)
library(car)
library(olsrr)
library(boot)
library(DHARMa)
library(dplyr)
library(plyr)
```


```{r}
#rawdat <- read.csv("../data/TA_Measurements_F75_working.csv")

rawdat <- read.csv("~/Desktop/Terry_flies/TA_Measurements_F75_working.csv")

#pixels per metre = 1.8599975E-06

# Turn my unmeasureables into NAs
index_50 <- which(rawdat$Length_px < 50)

rawdat$Length_px[index_50] <- NA

#Find and remove duplicate measures
length(rawdat$Label)
length(unique(rawdat$Label))
which(duplicated(rawdat$Label))

rawdat <- rawdat[-c(which(duplicated(rawdat$Label))),]

length(rawdat$Label)

length(unique(rawdat$Label))


# Convert to um from pixel
rawdat$length_um <- rawdat$Length_px * 1.8599975

rawdat$log_size <- log2(rawdat$length_um)
```

## Use filename labels variable to break into experimental variables

Also a bit of name clean up.

```{r}
rawdat_seperate <- separate(rawdat, 
                            col = Label, 
                            into = c("Imager","Replicate","Cohort","Sex","Trait", "Individual"), sep = "_")

rawdat_seperate$Individual <- gsub(x = rawdat_seperate$Individual,
                                   pattern = ".tif", 
                                   replacement = "")

rawdat_seperate$Cohort <- gsub(x = rawdat_seperate$Cohort,
                                   pattern = "C", 
                                   replacement = "")
```

## Using Table to see the sample sizes and if they are what you expect by groups

Just looking at heads, as I assume the sample sizes will be almost identical by traits. i.e. most traits were measurable on most individuals.

```{r}
with(rawdat_seperate[rawdat_seperate$Trait == "HEAD",], 
     table(interaction(Replicate, Sex, drop = T), Cohort))
```



## Getting setup to make a wide data frame

First we need to make the individual fly identifier (fly_id).

Then we simply our lives by making a svelte version of the dataset without some of the variables we don't need for the analysis (like length in px)

```{r}
rawdat_seperate$fly_id <- paste(rawdat_seperate$Replicate, 
                                 rawdat_seperate$Cohort, 
                                 rawdat_seperate$Sex, 
                                 rawdat_seperate$Individual,
                                sep = "_")

names(rawdat_seperate)

rawdat_simple <- rawdat_seperate[, c(3,4,5,6,10,11)]

### Trying to fix sex here

rawdat_simple$fly_id <- gsub("UCTR2_0_F_10", "UCTR2_0_M_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("UCTR4_2_F_15", "UCTR4_2_M_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("NTR1_1_M_19", "NTR1_1_F_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("NTR1_2_F_10", "NTR1_2_M_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("NTR1_2_F_12", "NTR1_2_M_22", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("NTR1_2_F_7", "NTR1_2_M_23", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("NTR2_2_F_19", "NTR2_2_M_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("NTR3_0_F_15", "NTR3_0_M_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("NTR3_0_F_16", "NTR3_0_M_22", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("NTR3_0_F_3", "NTR3_0_M_23", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("NTR4_0_F_20", "NTR4_0_M_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("SCTR2_0_F_3", "SCTR2_0_M_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("SCTR1_0_M_6", "SCTR1_0_F_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("SCTR2_1_M_4", "SCTR2_1_F_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("SCTR2_2_F_4", "SCTR2_2_M_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("SCTR3_1_M_14", "SCTR3_1_F_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("UCTR1_0_F_20", "UCTR1_0_M_21", rawdat_simple$fly_id)

rawdat_simple$fly_id <- gsub("UCTR1_2_F_7", "UCTR1_2_M_21", rawdat_simple$fly_id)

#### Sex has been corrected in fly_id, now to remove old columns, reseperate out fly_id and then recreate fly_id

# I swear this seems easier than doing this in excel.

rawdat_simple <- rawdat_simple[,-c(1:3)]

rawdat_simple <- separate(rawdat_simple, 
                            col = fly_id, 
                            into = c("Replicate","Cohort","Sex","Individual"), sep = "_")

rawdat_seperate$fly_id <- paste(rawdat_seperate$Replicate, 
                                 rawdat_seperate$Cohort, 
                                 rawdat_seperate$Sex, 
                                 rawdat_seperate$Individual,
                                sep = "_")


## re-check sample sizes since sex changed sample sizes

with(rawdat_simple[rawdat_simple$Trait == "HEAD",], 
     table(interaction(Replicate, Sex, drop = T), Cohort))

##


wide_fly <- as.data.frame(pivot_wider(rawdat_simple, 
                                      names_from = "Trait",
                                      values_from = "log_size"))

head(wide_fly)

wide_fly <- wide_fly %>%
  separate(Replicate, 
           into = c("Treatment", "Replicate"), 
           sep = "(?<=[A-Za-z])(?=[0-9])"
           )

colnames(wide_fly) <- tolower(colnames(wide_fly))

wide_fly$cohort <- as.numeric(wide_fly$cohort)
```



## some checks to make sure all the data is there as expected

Structure of missing data.

Sept 22/22: TA and I looked and the images seem to be missing from the measurement set. TA will check the computer.

```{r}
missing_by_row <- apply(wide_fly, MARGIN = 1, anyNA)

dim(wide_fly)

length(missing_by_row )

temp_dat <- wide_fly[missing_by_row ,]
```

Summary statistics and stuff


**Note from Ian, use apply functions to make your life easier for this**


NOTE FROM ID, checked min, max and mean for each of the treatment units nothing seems terribly amiss.

``` {r}
# for a matrix or array, apply can be super useful
apply(wide_fly[, 6:11], MARGIN = 2, quantile, na.rm = TRUE)
# or sapply will do the same since this is a data.frame we are using
sapply(wide_fly[, 6:11], quantile, na.rm = TRUE)

with(wide_fly, 
     tapply(head, 
            INDEX = list(interaction(treatment, replicate, drop = T), cohort, sex), 
            max, na.rm = TRUE))

with(wide_fly, 
     tapply(thorax, 
            INDEX = list(interaction(treatment, replicate, drop = T), cohort, sex), 
            max, na.rm = TRUE))

with(wide_fly, 
     tapply(wing, 
            INDEX = list(interaction(treatment, replicate, drop = T), cohort, sex), 
            max, na.rm = TRUE))

with(wide_fly, 
     tapply(femur, 
            INDEX = list(interaction(treatment, replicate, drop = T), cohort, sex), 
            max, na.rm = TRUE))

with(wide_fly, 
     tapply(tibia, 
            INDEX = list(interaction(treatment, replicate, drop = T), cohort, sex), 
            max, na.rm = TRUE))

with(wide_fly, 
     tapply(tarsus, 
            INDEX = list(interaction(treatment, replicate, drop = T), cohort, sex), 
            max, na.rm = TRUE))


skim(wide_fly)
```


## Plots of the raw data

**NOTE FROM ID:** For these plots you may find it easier to use the long data as you can facet_wrap on trait. I have not added it in.

```{r}
# Basic code and I just change the trait in question in the code to look at different traits

#Trait by sex histogram
ggplot(wide_fly, aes(x = femur, fill = treatment)) +
  facet_wrap(vars(sex)) +
  geom_histogram(binwidth = 0.05, alpha = 0.8)


# ID: I added this in
ggplot(wide_fly, aes(x = femur, colour = treatment)) +
  geom_density(alpha = 0.7) + 
  facet_wrap(vars(sex))

# NOTE FROM ID: but you may find ridge plots easier to see
ggplot(wide_fly, aes(x = femur, y = treatment, colour = treatment)) +
  geom_density_ridges(alpha = 0.5) + 
  facet_wrap(vars(sex))

#Comparison of cohorts and the effect on size

ggplot(wide_fly, aes(x = cohort, y = head, colour = treatment)) +
  geom_quasirandom(alpha = 0.4) +
  geom_smooth() +
  facet_wrap(vars(sex))

#Comparison of cohorts across treatments, sex and replicate

ggplot(wide_fly, aes(x = replicate, y = head, colour = as.factor(cohort))) +
  geom_quasirandom(alpha = 0.4) +
  facet_wrap(vars(treatment, sex))

ggplot(wide_fly, aes(x = replicate, y = thorax, colour = as.factor(cohort))) +
  geom_quasirandom(alpha = 0.4) +
  facet_wrap(vars(treatment, sex))

ggplot(wide_fly, aes(x = replicate, y = wing, colour = as.factor(cohort))) +
  geom_quasirandom(alpha = 0.4) +
  facet_wrap(vars(treatment, sex))


ggplot(wide_fly, aes(x = replicate, y = femur, colour = as.factor(cohort))) +
  geom_quasirandom(alpha = 0.4) +
  facet_wrap(vars(treatment, sex))

ggplot(wide_fly, aes(x = replicate, y = tibia, colour = as.factor(cohort))) +
  geom_quasirandom(alpha = 0.4) +
  facet_wrap(vars(treatment, sex))

ggplot(wide_fly, aes(x = replicate, y = tarsus, colour = as.factor(cohort))) +
  geom_quasirandom(alpha = 0.4) +
  facet_wrap(vars(treatment, sex))

# Comparison between two traits and if they differ in the sexes or in the cohorts
ggplot(wide_fly, aes(y = femur, x = thorax, colour = treatment)) +
     geom_jitter(width = 0, height = 0.3, alpha = 0.5) +
  facet_grid(vars(cohort, sex)) +
  geom_smooth(method = lm)
```

Fitting models

```{r}

#relevel sex
wide_fly$sex <- as.factor(wide_fly$sex)
wide_fly$sex <- relevel(wide_fly$sex, "M")

# Relevelling my treatments so that controls are the base level and my 'middle' treatment of UCT is the middle when plotting via emmeans and emtrends

wide_fly$treatment <- factor(wide_fly$treatment)
wide_fly$treatment <- relevel(wide_fly$treatment, "NTR")
wide_fly$replicate <- as.factor(wide_fly$replicate)

# centre thorax
wide_fly$thorax_c <- scale(wide_fly$thorax, 
                           center = TRUE, scale = FALSE)


# Is thorax changing (so does it remain a useful covariate)?
thorax_model1 <- glmmTMB(thorax ~ (sex + treatment + cohort)^2
                        + diag(1 + cohort| treatment:replicate), 
                              data = wide_fly)

summary(thorax_model1)
car::Anova(thorax_model1)


#wing model
wing_Allometry <- glmmTMB(wing ~ (sex + treatment + thorax_c)^3
                        + diag(1 + thorax_c | treatment:replicate), 
                              data = wide_fly)

summary(wing_Allometry)
car::Anova(wing_Allometry)

# head
head_Allometry <- glmmTMB(head~ (sex + treatment + thorax_c)^3
                        + diag(1 + thorax_c | treatment:replicate), 
                              data = wide_fly)

summary(head_Allometry)
car::Anova(head_Allometry)


# femur
femur_Allometry <- glmmTMB(femur ~ (sex + treatment + thorax_c)^3
                        + diag(1 + thorax_c | treatment:replicate), 
                              data = wide_fly)

summary(femur_Allometry)
car::Anova(femur_Allometry)

#Tibia model
tibia_Allometry <- glmmTMB(tibia ~ (sex + treatment + thorax_c)^3
                        + diag(1 + thorax_c | treatment:replicate), 
                              data = wide_fly)

summary(tibia_Allometry)
car::Anova(tibia_Allometry)


#tarsus
tarsus_Allometry <- glmmTMB(tarsus ~ (sex + treatment + thorax_c)^3
                        + diag(1 + thorax_c | treatment:replicate), 
                              data = wide_fly)

summary(tarsus_Allometry)
car::Anova(tarsus_Allometry)

```

Quick and dirty plots (will use effects and emmeans for the good plots)

```{r}
ggplot(wide_fly, 
       aes(y = tarsus, x = thorax, 
           color = treatment,
           shape = sex)) + geom_point(alpha = 0.5) +
  geom_smooth(aes(linetype = sex), method = "lm", alpha = 0.25) +
  xlab("Thorax Length (log2 um)")
  theme(legend.title = element_blank())
  

ggplot(wide_fly, 
       aes(y = wing, x = thorax, 
           color = treatment,
           shape = sex)) + geom_point(alpha = 0.5) +
  geom_smooth(aes(linetype = sex), method = "lm", alpha = 0.25) +
  xlab("Thorax Length (log2 um)")
  theme(legend.title = element_blank())  
  
ggplot(wide_fly, 
       aes(y = head, x = thorax, 
           color = treatment,
           shape = sex)) + geom_point(alpha = 0.5) +
  geom_smooth(aes(linetype = sex), method = "lm", alpha = 0.25) +
  xlab("Thorax Length (log2 um)") + 
  theme(legend.title = element_blank()) 
  
  
ggplot(wide_fly, 
       aes(y = femur, x = thorax, 
           color = treatment,
           shape = sex)) + geom_point(alpha = 0.5) +
  geom_smooth(aes(linetype = sex), method = "lm", alpha = 0.25) +
  xlab("Thorax Length (log2 um)") +
  theme(legend.title = element_blank())   

ggplot(wide_fly, 
       aes(y = tibia, x = thorax, 
           color = treatment,
           shape = sex)) + geom_point(alpha = 0.5) +
  geom_smooth(aes(linetype = sex), method = "lm", alpha = 0.25) +
  xlab("Thorax Length (log2 um)") +
  theme(legend.title = element_blank())   
```


How far from isometry vector for each replicate lineage and sex?
```{r}
dummy_code <- with(wide_fly, 
                   interaction(replicate, treatment, sex,
                               drop = T))

VCV_matrices <- with(wide_fly, 
     by(wide_fly[, c(6:11)], 
   dummy_code,
   function(x) cov(x, use = "pairwise.complete.obs")))

# correlation matrices just to look at
print(lapply(VCV_matrices, function(x) cov2cor(x) ), digits = 2)

# proportion of variance accounted for by each eigenvalue
eig_vals_mats <- sapply(VCV_matrices, function(x) svd(x)$d/sum(svd(x)$d))

print(eig_vals_mats, digits = 2)

# principal eigenvector
eig_vecs_mats <- sapply(VCV_matrices, function(x) eigen(x)$vectors[,1])
print(eig_vecs_mats, digits = 2)

# FYI, the expectation for a vector of isometry would be coefficients of
print( rep(1/sqrt(6), 6), digits = 2)
```

