---
title: "TA_working_F35_analysis"
output: html_document
date: "2023-04-05"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(digits = 3)
```


```{r}
library(effects)
library(grid)
library(tidyr)
library(ggplot2)
library(ggbeeswarm)
library(ggridges)
library(glmmTMB)
library(emmeans)
library(effects)
library(dotwhisker)
library(car)
library(olsrr)
library(boot)
library(DHARMa)
library(cowplot)
library(dplyr)
library(plyr)
```


Loading in data and doing basic data cleaning

```{r}

rawdat <- read.csv("../data/Audet_2022_terryflies.csv")
tarsus_dat <- read.csv("../data/tarsus_ConditionData.csv")
tarsus_dat$Trait <- "tarsus"
tarsus_dat <- tarsus_dat[,c(3,4,5,6,7,8,9,10,16,17,18,19,10,20)]

headers <- colnames(rawdat)
colnames(tarsus_dat) <- headers

with(tarsus_dat[tarsus_dat$NewTrait == "tarsus",], 
     table(interaction(Replicate, Sex, Treatment, drop = T), Cohort))

tarsus_dat <- tarsus_dat[!duplicated(tarsus_dat[,1:8]),]


rawdat <- rbind(tarsus_dat,rawdat)

rawdat$length_uM <- rawdat$length_mm*1000

rawdat$log_size <- log2(rawdat$length_uM)



# check sample sizes
with(rawdat[rawdat$NewTrait == "tarsus",], 
     table(interaction(Replicate, Sex, Treatment, drop = T), Cohort))
# sample sizes are perfect


# Make data wide
rawdat$fly_id <- paste(rawdat$Replicate, 
                                 rawdat$Cohort0, 
                                 rawdat$Sex,
                                 rawdat$Individual,
                                sep = "_")


rawdat_simple <- rawdat[, c(2,3,6,7,13,14,16,17)]

rawdat_simple <- separate(rawdat_simple, 
                            col = fly_id, 
                            into = c("Replicate","Cohort","Sex","Individual"), sep = "_")


# recheck sample sizes
with(rawdat_simple[rawdat_simple$NewTrait == "head",], 
     table(interaction(Replicate, Sex, drop = T), Cohort))
#

wide_fly <- as.data.frame(pivot_wider(rawdat_simple, 
                                      names_from = "NewTrait",
                                      values_from = "log_size"))

colnames(wide_fly) <- tolower(colnames(wide_fly))

wide_fly$cohort <- as.numeric(wide_fly$cohort)

wide_fly$thorax_c <- wide_fly$thorax - mean(wide_fly$thorax)


```

Make sure it appears all the data is as expected

```{r}

sum(apply(wide_fly, MARGIN = 1, anyNA))

dim(wide_fly)

```



``` {r}
# for a matrix or array, apply can be super useful
f35_stats <- apply(wide_fly[, 7:11], MARGIN = 2, quantile, na.rm = TRUE)
# or sapply will do the same since this is a data.frame we are using
sapply(wide_fly[, 7:11], quantile, na.rm = TRUE)

with(wide_fly, 
     tapply(head, 
            INDEX = list(interaction(treatment, replicate, drop = T), cohort, sex), 
            max, na.rm = TRUE))

with(wide_fly, 
     tapply(thorax, 
            INDEX = list(interaction(treatment, replicate, drop = T), cohort, sex), 
            max, na.rm = TRUE))

with(wide_fly, 
     tapply(winglength, 
            INDEX = list(interaction(treatment, replicate, drop = T), cohort, sex), 
            max, na.rm = TRUE))

with(wide_fly, 
     tapply(femur, 
            INDEX = list(interaction(treatment, replicate, drop = T), cohort, sex), 
            max, na.rm = TRUE))

with(wide_fly, 
     tapply(tibia, 
            INDEX = list(interaction(treatment, replicate, drop = T), cohort, sex), 
            max, na.rm = TRUE))

with(wide_fly, 
     tapply(tarsus, 
            INDEX = list(interaction(treatment, replicate, drop = T), cohort, sex), 
            max, na.rm = TRUE))
#skim(wide_fly)
```

Plot raw data sizes for supplement


```{r}

narrow_fly <- as.data.frame(pivot_longer(wide_fly, cols = c("femur", "tibia", "winglength", "thorax", "head", "tarsus"), names_to = "trait", values_to = "log_size"))


narrow_fly$treatment<-as.factor(narrow_fly$treatment)
levels(narrow_fly$treatment) <- c("NT", "UCT", "SCT")

ggplot(narrow_fly, aes(x = as.factor(cohort), y = 2^(log_size), colour = treatment, shape = sex)) +
geom_point(alpha = 0.5, position = position_jitterdodge(
  jitter.width = 0.2,
  jitter.height = 0,
  dodge.width = 0.5)) +
  theme_bw() +
  labs(x = "Cohort", y = "Size µm") +
  scale_x_discrete(drop = FALSE) +
  facet_grid(trait~., scales="free")
```


The first thing I am going to do is model allometry

```{r}

str(wide_fly)

# Set my factors and relevel data for model interpretation

wide_fly$sex <- as.factor(wide_fly$sex)
wide_fly$sex <- relevel(wide_fly$sex, "F")
wide_fly$cohort0 <- as.factor(wide_fly$cohort0)
wide_fly$cohort_n <- as.numeric(wide_fly$cohort0)
wide_fly$treatment <- factor(wide_fly$treatment)
wide_fly$treatment <- factor(wide_fly$treatment, levels = c("NT","UCT","SCT"))
wide_fly$replicate <- as.factor(wide_fly$replicate)

write.csv(wide_fly, "../data/F35_wideFly.csv", col.names = TRUE, row.names = FALSE)

# Wing length

wing_Allometry <- glmmTMB(winglength ~ (sex + treatment + thorax_c)^3
                        + diag(1 + sex + thorax_c | treatment:replicate), 
                              data = wide_fly)
summary(wing_Allometry)

wing_allo_supp <- plot(pairs(emtrends(wing_Allometry, ~treatment|sex, var = "thorax_c"))) +
  geom_vline(xintercept = 0, alpha = 0.5, linetype=2) +
  ylab("Wing") +
  xlab(NULL) +
  xlim(c(-0.25,0.25)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
  

pairs(emtrends(wing_Allometry, ~treatment, var = "thorax_c"))


car::Anova(wing_Allometry)


# Femur

femur_Allometry <- glmmTMB(femur ~ (sex + treatment + thorax_c)^3
                        + diag(1 + sex + thorax_c | treatment:replicate), 
                              data = wide_fly)
summary(femur_Allometry)

femur_allo_supp <- plot(pairs(emtrends(femur_Allometry, ~treatment|sex, var = "thorax_c"))) +
  geom_vline(xintercept = 0, alpha = 0.5, linetype=2) +
  ylab("Femur") +
  xlab(NULL) +
  xlim(c(-0.25,0.25)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

car::Anova(femur_Allometry)

# Tibia

tibia_Allometry <- glmmTMB(tibia ~ (sex + treatment + thorax_c)^3
                        + diag(1 + sex + thorax_c | treatment:replicate), 
                              data = wide_fly)
summary(tibia_Allometry)

tibia_allo_supp <- plot(pairs(emtrends(tibia_Allometry, ~treatment|sex, var = "thorax_c"))) +
  geom_vline(xintercept = 0, alpha = 0.5, linetype=2) +
  ylab("Tibia") +
  xlab(NULL) +
  xlim(c(-0.25,0.25)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

car::Anova(tibia_Allometry)

head_Allometry <- glmmTMB(head ~ (sex + treatment + thorax_c)^3
                        + diag(1 + sex + thorax_c | treatment:replicate), 
                              data = wide_fly)
summary(head_Allometry)


head_allo_supp <- plot(pairs(emtrends(head_Allometry, ~treatment|sex, var = "thorax_c"))) +
  geom_vline(xintercept = 0, alpha = 0.5, linetype=2) +
  ylab("Head") +
  xlab(NULL) +
  xlim(c(-0.25,0.25)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

car::Anova(head_Allometry)


tarsus_Allometry <- glmmTMB(tarsus ~ (sex + treatment + thorax_c)^3
                        + diag(1 + sex + thorax_c | treatment:replicate), 
                              data = wide_fly)
summary(tarsus_Allometry)


tarsus_allo_supp <- plot(pairs(emtrends(tarsus_Allometry, ~treatment|sex, var = "thorax_c"))) +
  geom_vline(xintercept = 0, alpha = 0.5, linetype=2) +
  ylab("Tarsus") +
  xlab("Estimate contrast") +
  #xlab(NULL) +
  xlim(c(-0.25,0.25))

plot_grid(wing_allo_supp,head_allo_supp,femur_allo_supp,tibia_allo_supp,tarsus_allo_supp,ncol = 1, rel_heights = c(1.9,1.9,1.9,1.9,2.4))


car::Anova(tarsus_Allometry)
```

Looking for size trends relative to thorax size for each trait

```{r}

wing_trend <- cbind(as.data.frame(emtrends(wing_Allometry, ~treatment|sex, var = "thorax_c")), trait=c("wing"))
femur_trend <- cbind(as.data.frame(emtrends(femur_Allometry, ~treatment|sex, var = "thorax_c")), trait=c("femur"))
tibia_trend <- cbind(as.data.frame(emtrends(tibia_Allometry, ~treatment|sex, var = "thorax_c")), trait=c("tibia"))
head_trend <- cbind(as.data.frame(emtrends(head_Allometry, ~treatment|sex, var = "thorax_c")), trait=c("head"))
tarsus_trend <- cbind(as.data.frame(emtrends(tarsus_Allometry, ~treatment|sex, var = "thorax_c")), trait=c("tarsus"))

trends <- as.data.frame(rbind(wing_trend,head_trend,femur_trend,tibia_trend, tarsus_trend))



trends$trait <- factor(trends$trait, levels = c("wing", "head", "femur", "tibia", "tarsus"))
trends$treatment <- factor(trends$treatment, levels = c("SCT", "UCT", "NT"))


F35_allometry <- ggplot(trends, aes(x=thorax_c.trend, y = treatment, shape = sex, colour = treatment)) +
  theme_classic() +
  facet_grid(trait~sex) +
  geom_linerange(aes(xmin=lower.CL,xmax=upper.CL), position = position_dodge(width = 0.90)) +
  geom_point(position = position_dodge(width = 0.90)) +
  xlab("Allometric slope") +
  ylab("Treatment") +
  theme(legend.position = "none") +
  scale_colour_grey(start = 0,end = 0.75,aesthetics = "colour")

```



Next I want to model changes in condition dependence. First I model it as a factor to find estimated mean sizes for each condition. (This is mostly for plotting cohort sizes)

```{R}

#wing model

wide_fly$cohort_factor <- as.factor(wide_fly$cohort0)

wing_Condition_f <- glmmTMB(winglength ~ (sex + treatment + cohort_factor)^3
                        + diag(1 + thorax_c + cohort_factor | treatment:replicate), 
                              data = wide_fly)


summary(wing_Condition_f)


car::Anova(wing_Condition_f)

wing_means_f <- as.data.frame(emmeans(wing_Condition_f, specs = c("cohort_factor", "treatment", "sex")))


wing_condition_supp <- plot(pairs(emmeans(wing_Condition_f, ~treatment|sex, var = "cohort_factor"))) +
  geom_vline(xintercept = 0, alpha = 0.5, linetype=2) +
  ylab("Wing") +
  xlab(NULL) +
  xlim(c(-0.1,0.1)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

wing_condition_plot <- ggplot(wing_means_f, aes(x = cohort_factor, y = 2^(emmean), colour = treatment, shape = sex)) +
  geom_linerange(aes(ymin = 2^(lower.CL), ymax = 2^(upper.CL)), position = position_dodge(width = 0.4), show.legend = FALSE) +
  ggtitle("Wing") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  xlab("Days Starved") +
  ylab(NULL) +
  geom_point(position = position_dodge(width = 0.4),show.legend = FALSE) +
  scale_colour_grey(start = 0.75,end = 0,aesthetics = "colour")

```

Below is a code chunk with the comparison of SSD between treatments and cohorts

```{r}

# Reaction norm plot

#emmip(wing_Condition_f,   treatment + sex ~ #cohort_factor, CIs = TRUE) + 
#  ylab("estimated trait value (log2, microM)") +
#  xlab("cohort")


emmeans_for_SSD_contrast_wing <- emmeans(wing_Condition_f, pairwise ~sex | treatment + cohort_factor)


SSD_contrasts_wing_SepByCondition <- contrast(emmeans_for_SSD_contrast_wing[[1]], 
                          interaction = c(treatment = "trt.vs.ctrl1"), 
                          by = "cohort_factor")

SSD_contrasts_wing <- contrast(emmeans_for_SSD_contrast_wing[[1]], 
                          interaction = c(treatment = "trt.vs.ctrl1", cohort_factor = "trt.vs.ctrl1"), 
                          by = NULL)

plot(SSD_contrasts_wing)

wing_SSD <- as.data.frame(SSD_contrasts_wing)

base_wing <- as.data.frame(as.data.frame(confint(emmeans_for_SSD_contrast_wing$contrasts)))


#  plotting contrast

wing_contrast_plot <- ggplot(confint(SSD_contrasts_wing), aes(x=estimate, y=treatment_trt.vs.ctrl1, colour=cohort_factor_trt.vs.ctrl1)) +
  geom_pointrange(aes(xmin = upper.CL, xmax = lower.CL), position = position_dodge(width=0.75), size = 0.25) +
  ylab("Wing") +
  xlab(NULL) +
  geom_vline(xintercept = 0, lty = 2 , alpha = 0.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  scale_colour_grey(start = 0.5, end = 0) +
  xlim(c(-0.075,0.075)) +
  theme(axis.ticks = element_blank(), axis.text.x = element_blank(), legend.position = "none")



# Plotting a different way but not for the stats
wing_SSD_plot <- ggplot(base_wing, aes(x = cohort_factor, y = estimate,colour = treatment, group = treatment)) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), show.legend = FALSE, position = position_dodge(width = 0.4), width = .1) +
  theme(legend.position="none") +
  ggtitle("Wing") +
  xlab(NULL) +
  ylab(NULL) +
  theme_classic() +
  geom_line(position = position_dodge(width = 0.4), show.legend = FALSE)


```


Head response to condition as a factor

```{r}
# head
head_Condition_f <- glmmTMB(head ~ (sex + treatment + cohort_factor)^3
                            + diag(1 + thorax_c + cohort_factor | treatment:replicate),
                            data = wide_fly)

summary(head_Condition_f)
car::Anova(head_Condition_f)

head_means_f <- as.data.frame(emmeans(head_Condition_f, specs = c("cohort_factor", "treatment", "sex")))

head_condition_supp <- plot(pairs(emmeans(head_Condition_f, ~treatment|sex, var = "cohort_factor"))) +
  geom_vline(xintercept = 0, alpha = 0.5, linetype=2) +
  ylab("Head") +
  xlab(NULL) +
  xlim(c(-0.1,0.1)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

head_condition_plot <- ggplot(head_means_f, aes(x = cohort_factor, y = 2^(emmean), colour = treatment, shape = sex)) +
  geom_linerange(aes(ymin = 2^(lower.CL), ymax = 2^(upper.CL)), position = position_dodge(width = 0.4), show.legend = FALSE) +
  ylab("Length (\u00B5m)") +
  ggtitle("Head") +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Days starved") +
  theme(legend.position="none") +
  theme_classic() +
  geom_point(position = position_dodge(width = 0.4), show.legend = FALSE) +
  scale_colour_grey(start = 0.75,end = 0,aesthetics = "colour")

```

Head SSD comparison

```{r}
emmeans_for_SSD_contrast_head <- emmeans(head_Condition_f, pairwise ~sex | treatment + cohort_factor)


SSD_contrasts_head_byTreat <- contrast(emmeans_for_SSD_contrast_head[[1]], 
                          interaction = c(treatment = "trt.vs.ctrl1"), 
                          by = "cohort_factor")

as.data.frame(as.data.frame(SSD_contrasts_head_byTreat))

SSD_contrasts_head <- contrast(emmeans_for_SSD_contrast_head[[1]], 
                          interaction = c(treatment = "trt.vs.ctrl1", cohort_factor = "trt.vs.ctrl1"), 
                          by = NULL)

head_SSD <- as.data.frame(SSD_contrasts_head)

base_head <- as.data.frame(as.data.frame(confint(emmeans_for_SSD_contrast_head$contrasts)))



# Plotting
head_contrast_plot <- ggplot(confint(SSD_contrasts_head), aes(x=estimate, y=treatment_trt.vs.ctrl1, colour=cohort_factor_trt.vs.ctrl1)) +
  geom_pointrange(aes(xmin = upper.CL, xmax = lower.CL), position = position_dodge(width=0.75), size = 0.25) +
  ylab("Head") +
  xlab(NULL) +
  geom_vline(xintercept = 0, lty = 2 , alpha = 0.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  scale_colour_grey(start = 0.5, end = 0) +
  xlim(c(-0.075,0.075)) +
  theme(axis.ticks = element_blank(), axis.text.x = element_blank(), legend.position = "none")

# Plotting a different way but not for the stats
head_SSD_plot <- ggplot(base_head, aes(x = cohort_factor, y = estimate,colour = treatment, group = treatment)) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), show.legend = FALSE, position = position_dodge(width = 0.4), width = .1) +
  theme(legend.position="none") +
  ggtitle("Head") +
  xlab(NULL) +
  ylab(NULL) +
  theme_classic() +
  geom_line(position = position_dodge(width = 0.4), show.legend = FALSE)
```

Femur response to condition as a factor

```{r}
# femur
femur_Condition_f <- glmmTMB(femur ~ (sex + treatment + cohort_factor)^3
                        + diag(1 + thorax_c + cohort_factor | treatment:replicate), 
                              data = wide_fly)

summary(femur_Condition_f)
car::Anova(femur_Condition_f)

femur_means_f <- as.data.frame(emmeans(femur_Condition_f, specs = c("cohort_factor", "treatment", "sex")))

femur_condition_supp <- plot(pairs(emmeans(femur_Condition_f, ~treatment|sex, var = "cohort_factor"))) +
  geom_vline(xintercept = 0, alpha = 0.5, linetype=2) +
  ylab("Femur") +
  xlab(NULL) +
  xlim(c(-0.1,0.1)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

femur_condition_plot <- ggplot(femur_means_f, aes(x = cohort_factor, y = 2^(emmean), colour = treatment, shape = sex)) +
  geom_linerange(aes(ymin = 2^(lower.CL), ymax = 2^(upper.CL)), position = position_dodge(width = 0.4), show.legend = FALSE) +
  ylab("Length (\u00B5m)") +
  ggtitle("Femur") +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab(NULL) +
  theme(legend.position="none") +
  theme_classic() +
  geom_point(position = position_dodge(width = 0.4), show.legend = FALSE) +
  scale_colour_grey(start = 0.75,end = 0,aesthetics = "colour")

```

Femur SSD comparison
```{r}
emmeans_for_SSD_contrast_femur <- emmeans(femur_Condition_f, pairwise ~sex | treatment + cohort_factor)


SSD_contrasts_femur_bytreat <- contrast(emmeans_for_SSD_contrast_femur[[1]], 
                          interaction = c(treatment = "trt.vs.ctrl1"), 
                          by = "cohort_factor")

as.data.frame(as.data.frame(SSD_contrasts_femur_bytreat))

SSD_contrasts_femur <- contrast(emmeans_for_SSD_contrast_femur[[1]], 
                          interaction = c(treatment = "trt.vs.ctrl1", cohort_factor = "trt.vs.ctrl1"), 
                          by = NULL)

femur_SSD <- as.data.frame(SSD_contrasts_femur)

base_femur <- as.data.frame(as.data.frame(confint(emmeans_for_SSD_contrast_femur$contrasts)))



# Plotting
femur_contrast_plot <- ggplot(confint(SSD_contrasts_femur), aes(x=estimate, y=treatment_trt.vs.ctrl1, colour=cohort_factor_trt.vs.ctrl1)) +
  geom_pointrange(aes(xmin = upper.CL, xmax = lower.CL), position = position_dodge(width=0.75), size = 0.25) +
  ylab("Femur") +
  xlab(NULL) +
  geom_vline(xintercept = 0, lty = 2 , alpha = 0.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  scale_colour_grey(start = 0.5, end = 0) +
  xlim(c(-0.075,0.075)) +
  theme(axis.ticks = element_blank(), axis.text.x = element_blank(), legend.position = "none")

# Plotting a different way but not for the stats
femur_SSD_plot <- ggplot(base_femur, aes(x = cohort_factor, y = estimate,colour = treatment, group = treatment)) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), show.legend = FALSE, position = position_dodge(width = 0.4), width = .1) +
  theme(legend.position="none") +
  ggtitle("Femur") +
  xlab(NULL) +
  ylab(NULL) +
  theme_classic() +
  geom_line(position = position_dodge(width = 0.4), show.legend = FALSE)
```

Tibia response to condition as a factor
```{r}
#Tibia model
tibia_Condition_f <- glmmTMB(tibia ~ (sex + treatment + cohort_factor)^3
                        + diag(1 + thorax_c + cohort_factor | treatment:replicate), 
                              data = wide_fly)

summary(tibia_Condition_f)
car::Anova(tibia_Condition_f)

tibia_means_f <- as.data.frame(emmeans(tibia_Condition_f, specs = c("cohort_factor", "treatment", "sex")))

tibia_condition_supp <- plot(pairs(emmeans(tibia_Condition_f, ~treatment|sex, var = "cohort_factor"))) +
  geom_vline(xintercept = 0, alpha = 0.5, linetype=2) +
  ylab("Tibia") +
  xlab(NULL) +
  xlim(c(-0.1,0.1)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

tibia_condition_plot <- ggplot(tibia_means_f, aes(x = cohort_factor, y = 2^(emmean), colour = treatment, shape = sex)) +
  geom_linerange(aes(ymin = 2^(lower.CL), ymax = 2^(upper.CL)), position = position_dodge(width = 0.4), show.legend = FALSE) +
  ggtitle("Tibia") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab(NULL) +
  xlab(NULL) +
  theme(legend.position="none") +
  theme_classic() +
  geom_point(position = position_dodge(width = 0.4), show.legend = FALSE) +
  scale_colour_grey(start = 0.75,end = 0,aesthetics = "colour")

```

Tibia SSD comparison
```{r}
emmeans_for_SSD_contrast_tibia <- emmeans(tibia_Condition_f, pairwise ~sex | treatment + cohort_factor)

SSD_contrasts_tibia_bytreat <- contrast(emmeans_for_SSD_contrast_tibia[[1]], 
                          interaction = c(treatment = "trt.vs.ctrl1"), 
                          by = "cohort_factor")

as.data.frame(as.data.frame(SSD_contrasts_tibia_bytreat))

SSD_contrasts_tibia <- contrast(emmeans_for_SSD_contrast_tibia[[1]], 
                          interaction = c(treatment = "trt.vs.ctrl1", cohort_factor = "trt.vs.ctrl1"), 
                          by = NULL)

tibia_SSD <- as.data.frame(SSD_contrasts_tibia)

base_tibia <- as.data.frame(as.data.frame(confint(emmeans_for_SSD_contrast_tibia$contrasts)))


# Plotting
tibia_contrast_plot <- ggplot(confint(SSD_contrasts_tibia), aes(x=estimate, y=treatment_trt.vs.ctrl1, colour=cohort_factor_trt.vs.ctrl1)) +
  geom_pointrange(aes(xmin = upper.CL, xmax = lower.CL), position = position_dodge(width=0.75), size = 0.25) +
  ylab("Tibia") +
  xlab(NULL) +
  geom_vline(xintercept = 0, lty = 2 , alpha = 0.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  scale_colour_grey(start = 0.5, end = 0) +
  xlim(c(-0.075,0.075)) +
  theme(axis.ticks = element_blank(), axis.text.x = element_blank(), legend.position = "none")

# Plotting a different way but not for the stats
tibia_SSD_plot <- ggplot(base_tibia, aes(x = cohort_factor, y = estimate,colour = treatment, group = treatment)) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), show.legend = FALSE, position = position_dodge(width = 0.4), width = .1) +
  theme(legend.position="none") +
  ggtitle("Tibia") +
  xlab(NULL) +
  ylab(NULL) +
  theme_classic() +
  geom_line(position = position_dodge(width = 0.4), show.legend = FALSE)
```

Tarsus response to condition

```{R}


tarsus_Condition_f <- glmmTMB(tarsus ~ (sex + treatment + cohort_factor)^3
                        + diag(1 + thorax_c + cohort_factor | treatment:replicate), 
                              data = wide_fly)


summary(tarsus_Condition_f)


car::Anova(tarsus_Condition_f)

tarsus_means_f <- as.data.frame(emmeans(tarsus_Condition_f, specs = c("cohort_factor", "treatment", "sex")))

tarsus_condition_supp <- plot(pairs(emmeans(tarsus_Condition_f, ~treatment|sex, var = "cohort_factor"))) +
  geom_vline(xintercept = 0, alpha = 0.5, linetype=2) +
  ylab("Tarsus") +
  xlab("Condition response contrast") +
  xlim(c(-0.1,0.1))

tarsus_condition_plot <- ggplot(tarsus_means_f, aes(x = cohort_factor, y = 2^(emmean), colour = treatment, shape = sex)) +
  geom_linerange(aes(ymin = 2^(lower.CL), ymax = 2^(upper.CL)), position = position_dodge(width = 0.4), show.legend = FALSE) +
  ggtitle("Tarsus") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  xlab(NULL) +
  ylab(NULL) +
  geom_point(position = position_dodge(width = 0.4),show.legend = FALSE) +
  scale_colour_grey(start = 0.75,end = 0,aesthetics = "colour")


```

Tarsus SSD

```{r}
emmeans_for_SSD_contrast_tarsus <- emmeans(tarsus_Condition_f, pairwise ~sex | treatment + cohort_factor)


SSD_contrasts_tarsus_bytreat <- contrast(emmeans_for_SSD_contrast_tarsus[[1]], 
                          interaction = c(treatment = "trt.vs.ctrl1"), 
                          by = "cohort_factor")

as.data.frame(as.data.frame(SSD_contrasts_tarsus_bytreat))

SSD_contrasts_tarsus <- contrast(emmeans_for_SSD_contrast_tarsus[[1]], 
                          interaction = c(treatment = "trt.vs.ctrl1", cohort_factor = "trt.vs.ctrl1"), 
                          by = NULL)

tarsus_SSD <- as.data.frame(SSD_contrasts_tarsus)

base_tarsus <- as.data.frame(as.data.frame(confint(emmeans_for_SSD_contrast_tarsus$contrasts)))


tarsus_contrast_plot <- ggplot(confint(SSD_contrasts_tarsus), aes(x=estimate, y=treatment_trt.vs.ctrl1, colour=cohort_factor_trt.vs.ctrl1)) +
  geom_pointrange(aes(xmin = upper.CL, xmax = lower.CL), position = position_dodge(width=0.85), size = 0.25) +
  ylab("Tarsus") +
  xlab("F-M contrast between treatment") +
  geom_vline(xintercept = 0, lty = 2 , alpha = 0.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  scale_colour_grey(start = 0.5, end = 0) +
  xlim(c(-0.075,0.075)) +
  theme(axis.ticks = element_blank(),legend.position = "none")



# Plotting a different way but not for the stats
tarsus_SSD_plot <- ggplot(base_tarsus, aes(x = cohort_factor, y = estimate,colour = treatment, group = treatment)) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), show.legend = FALSE, position = position_dodge(width = 0.4), width = .1) +
  theme(legend.position="none") +
  ggtitle("Tarsus") +
  xlab(NULL) +
  ylab(NULL) +
  theme_classic() +
  geom_line(position = position_dodge(width = 0.4), show.legend = FALSE)
```

SSD contrast plot
```{r}

plot1 <- plot_grid(wing_contrast_plot,head_contrast_plot,femur_contrast_plot,tibia_contrast_plot,tarsus_contrast_plot,ncol = 1,rel_heights = c(0.65,0.65,0.65,0.65,1))


dummy_plot <- ggplot(confint(SSD_contrasts_tarsus), aes(x=estimate, y=treatment_trt.vs.ctrl1, colour=cohort_factor_trt.vs.ctrl1)) +
  geom_pointrange(aes(xmin = upper.CL, xmax = lower.CL), position = position_dodge(width=0.85), size = 0.25) +
  ylab("Tarsus") +
  xlab("F-M contrast between treatment") +
  geom_vline(xintercept = 0, lty = 2 , alpha = 0.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title = "Days starved contrast") +
  theme_classic() +
  scale_colour_grey(start = 0.5, end = 0) +
  xlim(c(-0.075,0.075)) +
  theme(axis.ticks = element_blank()) +
  guides(colour=guide_legend("Days\nstarved\ncontrast"))
    

legend <- get_legend(dummy_plot)

plot_grid(plot1,legend,rel_widths = c(1,0.2))

```


Below I plot all estimated trait means and response to condition together with cowplot including a legend made from extracting them from two dummy plots
```{r}
dummy_plot <- ggplot(tibia_means_f, aes(x = cohort_factor, y = 2^(emmean), colour = treatment, shape = sex)) +
geom_linerange(aes(ymin = 2^(lower.CL), ymax = 2^(upper.CL)), position = position_dodge(width = 0.4), show.legend = FALSE) +
  ggtitle("Tarsus") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab(NULL) +
  xlab(NULL) +
  theme_classic() +
  guides(fill="none",shape="none") +
  guides(color = guide_legend(override.aes = list(size = 0.75))) +
  theme(legend.title = element_text(size = 5), 
               legend.text = element_text(size = 5)) +
  geom_point(position = position_dodge(width = 0.4)) +
  scale_colour_grey(start = 0.75,end = 0,aesthetics = "colour")


dummy_plot_2 <- ggplot(tibia_means_f, aes(x = cohort_factor, y = 2^(emmean), colour = treatment, shape = sex)) +
geom_linerange(aes(ymin = 2^(lower.CL), ymax = 2^(upper.CL)), position = position_dodge(width = 0.4), show.legend = FALSE) +
  ggtitle("Tarsus") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab(NULL) +
  xlab(NULL) +
  theme_classic() +
  guides(fill="none",colour="none") +
  #guides(color = guide_legend(override.aes = list(size = 0.75))) +
  theme(legend.title = element_text(size = 5), 
               legend.text = element_text(size = 5)) +
  geom_point(position = position_dodge(width = 0.4)) +
  scale_colour_grey(start = 0.75,end = 0,aesthetics = "colour")


treatment_legend <- get_legend(dummy_plot)
shape_legend <- get_legend(dummy_plot_2)

legend <- plot_grid(treatment_legend,shape_legend,ncol = 2, align = 'hv', axis = 'b', rel_widths = c(1, 1.5))

response_condition <- plot_grid(femur_condition_plot,tibia_condition_plot,tarsus_condition_plot,head_condition_plot,wing_condition_plot,axis = "t")


## plotting supplemental contrast

plot_grid(wing_condition_supp,head_condition_supp,femur_condition_supp,tibia_condition_supp,tarsus_condition_supp,ncol = 1)



```


Below I plot SSD without the condition contrast
```{r}
SSD_wing <- as.data.frame(as.data.frame(confint(emmeans_for_SSD_contrast_wing$contrasts)))
SSD_head <- as.data.frame(as.data.frame(confint(emmeans_for_SSD_contrast_head$contrasts)))
SSD_femur <- as.data.frame(as.data.frame(confint(emmeans_for_SSD_contrast_femur$contrasts)))
SSD_tibia <- as.data.frame(as.data.frame(confint(emmeans_for_SSD_contrast_tibia$contrasts)))
SSD_tarsus <- as.data.frame(as.data.frame(confint(emmeans_for_SSD_contrast_tarsus$contrasts)))

wing_SSD_plot <- ggplot(SSD_wing[SSD_wing$cohort_factor == 0,], aes(x=estimate, y=treatment, colour=cohort_factor)) +
  geom_pointrange(aes(xmin = upper.CL, xmax = lower.CL), position = position_dodge(width=0.85), size = 0.25) +
  ylab("Wing") +
  xlab(NULL) +
  geom_vline(xintercept = 0, lty = 2 , alpha = 0.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  scale_colour_grey(start = 0.5, end = 0) +
  xlim(c(-0.15,0.15)) +
  theme(axis.ticks = element_blank(),legend.position = "none")

head_SSD_plot <- ggplot(SSD_head[SSD_head$cohort_factor == 0,], aes(x=estimate, y=treatment, colour=cohort_factor)) +
  geom_pointrange(aes(xmin = upper.CL, xmax = lower.CL), position = position_dodge(width=0.85), size = 0.25) +
  ylab("Head") +
  xlab(NULL) +
  geom_vline(xintercept = 0, lty = 2 , alpha = 0.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  scale_colour_grey(start = 0.5, end = 0) +
  xlim(c(-0.15,0.15)) +
  theme(axis.ticks = element_blank(),legend.position = "none")

femur_SSD_plot <- ggplot(SSD_femur[SSD_femur$cohort_factor == 0,], aes(x=estimate, y=treatment, colour=cohort_factor)) +
  geom_pointrange(aes(xmin = upper.CL, xmax = lower.CL), position = position_dodge(width=0.85), size = 0.25) +
  ylab("Femur") +
  xlab(NULL) +
  geom_vline(xintercept = 0, lty = 2 , alpha = 0.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  scale_colour_grey(start = 0.5, end = 0) +
  xlim(c(-0.15,0.15)) +
  theme(axis.ticks = element_blank(),legend.position = "none")

tibia_SSD_plot <- ggplot(SSD_tibia[SSD_tibia$cohort_factor == 0,], aes(x=estimate, y=treatment, colour=cohort_factor)) +
  geom_pointrange(aes(xmin = upper.CL, xmax = lower.CL), position = position_dodge(width=0.85), size = 0.25) +
  ylab("Tibia") +
  xlab(NULL) +
  geom_vline(xintercept = 0, lty = 2 , alpha = 0.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  scale_colour_grey(start = 0.5, end = 0) +
  xlim(c(-0.15,0.15)) +
  theme(axis.ticks = element_blank(),legend.position = "none")

tarsus_SSD_plot <- ggplot(SSD_tarsus[SSD_tarsus$cohort_factor == 0,], aes(x=estimate, y=treatment, colour=cohort_factor)) +
  geom_pointrange(aes(xmin = upper.CL, xmax = lower.CL), position = position_dodge(width=0.85), size = 0.25) +
  ylab("Tarsus") +
  xlab(NULL) +
  geom_vline(xintercept = 0, lty = 2 , alpha = 0.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  scale_colour_grey(start = 0.5, end = 0) +
  xlim(c(-0.15,0.15)) +
  theme(axis.ticks = element_blank(),legend.position = "none")

F35_SSD <- plot_grid(femur_SSD_plot,tibia_SSD_plot,tarsus_SSD_plot,wing_SSD_plot,head_SSD_plot,ncol = 1)

```





Below I look at response to condition as a trend in each trait (numeric condition)

```{r}

#wing model

# Making cohort numeric so that I can model trends of condition
wide_fly$cohort_numeric <- as.numeric(wide_fly$cohort)

wing_Condition_mod1 <- glmmTMB(winglength ~ (sex + treatment + cohort_numeric)^3
                        + diag(1 + thorax_c + cohort_numeric | treatment:replicate), 
                              data = wide_fly)


summary(wing_Condition_mod1)

# getting estimated means for cohort - this is returning contrasts for some reason

wing_slopes_mod1 <- emtrends(wing_Condition_mod1, ~ treatment|sex, var = "cohort_numeric")

pairs(wing_slopes_mod1)

car::Anova(wing_Condition_mod1)


plot(wing_slopes_mod1)
# Female wings becoming less condition dependent in treatments
# Males not responding


wing_slope <- cbind(as.data.frame(wing_slopes_mod1), trait=c("wing"))


# head
head_Condition_n <- glmmTMB(head ~ (sex + treatment + cohort_numeric)^3 
                            + diag(1 + thorax_c + cohort_numeric | treatment:replicate), 
                              data = wide_fly)

summary(head_Condition_n)
# Minor interaction between condition sex and SCT
car::Anova(head_Condition_n)

head_slopes_mod1 <- emtrends(head_Condition_n, ~ treatment|sex, var = "cohort_numeric")

plot(head_slopes_mod1)
pairs(head_slopes_mod1)
# Female heads becoming less condition dependent in UCT
# Males unchanged, moving in direction of becoming less condition dependent

head_slope <- cbind(as.data.frame(head_slopes_mod1), trait=c("head"))


# femur
femur_Condition_n <- glmmTMB(femur ~ (sex + treatment + cohort_numeric)^3
                        + diag(1 + thorax_c + cohort_numeric | treatment:replicate), 
                              data = wide_fly)

summary(femur_Condition_n)
# No interaction sex:cohort:treatment
car::Anova(femur_Condition_n)
# no interaction sex:cohort:treatment

femur_slopes_mod1 <- emtrends(femur_Condition_n, ~ treatment|sex, var = "cohort_numeric")

plot(femur_slopes_mod1)
pairs(femur_slopes_mod1)
# Female femur unchanged, moving in different dorection in the two treatments
# Males unchanged

femur_slope <- cbind(as.data.frame(femur_slopes_mod1), trait=c("femur"))



#Tibia model
tibia_Condition_n <- glmmTMB(tibia ~ (sex + treatment + cohort_numeric)^3
                        + diag(1 + thorax_c + cohort_numeric | treatment:replicate), 
                              data = wide_fly)

summary(tibia_Condition_n)
car::Anova(tibia_Condition_n)
# No sex:treatment:condition interaction

tibia_slopes_mod1 <- emtrends(tibia_Condition_n, ~ treatment|sex, var = "cohort_numeric")

plot(tibia_slopes_mod1)
pairs(tibia_slopes_mod1)
# Females in SCT are more condition dependent for tibia
# Males unchanged

tibia_slope <- cbind(as.data.frame(tibia_slopes_mod1), trait=c("tibia"))

#Tarsus model
tarsus_Condition_n <- glmmTMB(tarsus ~ (sex + treatment + cohort_numeric)^3
                        + diag(1 + thorax_c + cohort_numeric | treatment:replicate), 
                              data = wide_fly)

summary(tarsus_Condition_n)
car::Anova(tarsus_Condition_n)
# No sex:treatment:condition interaction

tarsus_slopes_mod1 <- emtrends(tarsus_Condition_n, ~ treatment|sex, var = "cohort_numeric")

plot(tarsus_slopes_mod1)
pairs(tarsus_slopes_mod1)
# Females in SCT are more condition dependent for tibia
# Males unchanged

tibia_slope <- cbind(as.data.frame(tibia_slopes_mod1), trait=c("tibia"))
tarsus_slope <- cbind(as.data.frame(tarsus_slopes_mod1), trait=c("tarsus"))



con_trends <- as.data.frame(rbind(wing_slope,head_slope,femur_slope,tibia_slope,tarsus_slope))

con_trends$trait <- as.factor(con_trends$trait)

con_trends$trait <- factor(con_trends$trait, levels = c("wing", "head", "femur", "tibia", "tarsus"))
con_trends$treatment <- factor(con_trends$treatment, levels = c("SCT", "UCT", "NT"))
con_trends$cohort <- factor(con_trends$cohort, levels = c("2", "1", "0"))





# figure
trend_condition <- ggplot(con_trends, aes(x=cohort_numeric.trend, y = treatment, shape = sex, colour = treatment)) +
  geom_linerange(aes(xmin=lower.CL,xmax=upper.CL),position=position_dodge2(width = 0.9), show.legend = FALSE) +
  theme(strip.text.x = element_blank()) +
  theme_classic() +
  facet_wrap(~trait, ncol = 1, strip.position = "right") +
  ylab(NULL) +
  xlab("Slope of condition") +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.line.y = element_blank(), legend.position = "none") +
  geom_point(position = position_dodge2(width = 0.90), show.legend = FALSE) +
  scale_colour_grey(start = 0,end = 0.75,aesthetics = "colour")


first_plot <- plot_grid(response_condition,trend_condition,rel_widths = c(1,0.5))

F35_condition <- plot_grid(first_plot,rel_widths = c(1,0.1))

```


Below I plot the F35 SSD

```{r}

part_1 <- plot_grid(femur_SSD_plot,tibia_SSD_plot,tarsus_SSD_plot,wing_SSD_plot,head_SSD_plot,legend)

plot_grid(part_1,legend,rel_widths = c(1,0.1))



```


Just as a supplemental figure, I want to model thorax size between treatment groups.


```{R}


thorax_Condition_f <- glmmTMB(thorax_c ~ (sex + treatment + cohort_factor)^3
                        + diag(1 + cohort_factor | treatment:replicate), 
                              data = wide_fly)


summary(thorax_Condition_f)


car::Anova(tarsus_Condition_f)

thorax_means_f <- as.data.frame(emmeans(thorax_Condition_f, specs = c("cohort_factor", "treatment", "sex")))

thorax_condition_supp <- plot(pairs(emmeans(thorax_Condition_f, ~treatment|sex, var = "cohort_factor"))) +
  geom_vline(xintercept = 0, alpha = 0.5, linetype=2) +
  ylab("Thorax") +
  xlab("Condition response contrast") +
  xlim(c(-0.1,0.1))

thorax_condition_plot <- ggplot(thorax_means_f, aes(x = cohort_factor, y = 2^(emmean), colour = treatment, shape = sex)) +
  geom_linerange(aes(ymin = 2^(lower.CL), ymax = 2^(upper.CL)), position = position_dodge(width = 0.4), show.legend = FALSE) +
  ggtitle("Thorax F35") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  theme_classic() +
  ylab("Thorax size (mm)") +
  geom_point(position = position_dodge(width = 0.4)) +
  scale_colour_grey(start = 0.75,end = 0,aesthetics = "colour")


```
